Estimating duration in the presence of misclassification

### 2024-07-29 ATACCC.tex
ref section in another chapter correctly

Based on the fit to the data achieved when implementing an earlier version of the model (see \cref{ATACCC:sec:original-analysis}), I hypothesised that the cause of this was overcomplicating the model for test failures.
Specifically, excluding false positives from the model still explains the data well (see \cref{ATACCC:fig:goodness-of-fits}).
Furthermore, a prior that false negatives and false positives are equally likely is not supported by other information (see \cref{biology-data:sec:measurement-error}).
Therefore, I simplified the model for test failures to only false negatives.
% These false negatives could represent a variety of scenarios, such as poor swabbing technique.
Formally, I replaced \cref{ATACCC:eq:hakki-likelihood} with the following.
\begin{align}
p(y_{i,t} \mid \cdot) &= \begin{cases}
    (1 - \rho) f_N(y_{i,t} \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} > v_\text{lod}$}\\
    \rho + (1 - \rho) F_N(\vlod \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} = v_\text{lod}$.}
\end{cases}
\end{align}

>>>>

Based on the fit to the data achieved when implementing an earlier version of the model (see \cref{ATACCC:sec:original-analysis}), I hypothesised that the cause of this was overcomplicating the model for test failures.
Specifically, excluding false positives from the model still explains the data well (see \cref{ATACCC:fig:goodness-of-fits}).
Furthermore, a prior that false negatives and false positives are equally likely is not supported by other information (see \cref{E-biology-data:sec:measurement-error}).
Therefore, I simplified the model for test failures to only false negatives.
% These false negatives could represent a variety of scenarios, such as poor swabbing technique.
Formally, I replaced \cref{ATACCC:eq:hakki-likelihood} with the following.
\begin{align}
p(y_{i,t} \mid \cdot) &= \begin{cases}
    (1 - \rho) f_N(y_{i,t} \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} > v_\text{lod}$}\\
    \rho + (1 - \rho) F_N(\vlod \mid \log v_i(t), \sigma_v^2) & \text{if $y_{i,t} = v_\text{lod}$.}
\end{cases}
\end{align}
